\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-13 doc/sw-cfhtls.tex
read through all sections

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
potential lens candidates for the simulated sample. To avoid using a
known lens galaxy for our simulation purpose, we exclude all those
galaxies whose positions match with the lensing galaxies from the SARCS
samples within 2~arcsec.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
%{\bf fix the normalization}
}
\end{center}
\end{figure}

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of XXX (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

There are a total of XXX candidates with $1.3\le$G$<2$ (medium
probability sample) out of which 30 are new. The quality of candidates
in this category is such that at least one of the inspectors thought the
candidate is most probably a lens (that is, a grade of 2) and a second inspector
thought this is possibly a lens (that is, a grade of 1). Among our high
probability sample (G$\ge$2), there are a total of XXX candidates out of
which 28 are new. In this category, the minimum grade by all of the
inspectors was 2 suggesting that the candidates are probably or almost
certainly lenses according to all of the inspectors. To avoid
duplication, further information on \sw candidates that were previously
identified in the literature is available at
http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
candidates with G$\ge 1.3$ (medium-high probability) is presented in this paper (see
\Sref{sec:results:newcand}).

In Table~\ref{tab:stats}, we give overall statistics of the systems
detected at \StageOne and \StageTwo. We give the total number of
detections of the known lens candidates, known lenses and the new lens
candidates at each stage.  We also give the recovery fractions for the
known samples and fraction of total detection for the new samples at
each stage. We find that most (XXX check) of the confirmed lenses found
at \StageOne are also recovered at \StageTwo whereas a small fraction of
the known lens candidates are rejected at \StageTwo. Also, the sample of
new lens candidates increases the sample of \cfhtls lens candidates by
over 50\%.

In \Fref{fig:stackP}, we plot the distribution of false positives and
the high probability lens candidates, categorized by the lens experts,
as a function of the P value assigned by SWAP at the end of \StageTwo.
On average, the fraction of lens candidates is indeed an increasing
function of P. This shows that the \sw generated P values for the
subject are roughly correlated with the expert grades albeit with quite
some scatter.  We note that from P$\sim$0.75 onwards to lower P values,
the fraction of false positives starts to exceed the fraction of real
lens candidates. This could be a good threshold to choose to maximize
the purity of the final sample. However, we go with the choice of
P$=$0.3 as this gives a more acceptable completeness of XXX for the
known sample and thus, the new sample which combined with expert grading
allows us to achieve further purity of our sample.

%{\bf AM: give some numbers for the completeness/purity ? I will check what grades we gave to the stage 2 detected KLs and comment on it.}

@@

%{\bf Note:} $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional

>>>>

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[]{Gavazzi2014} as potential lens candidates for
the simulated sample. To avoid using a known lens galaxy for our
simulation purpose, we exclude all those galaxies whose positions match
with the lensing galaxies from the SARCS samples within 2~arcsec.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
}
\end{center}
\end{figure}

@@

In this section, we describe the \sw-\cfhtls lens sample (henceforth,
called the \sw lens sample). We find a total of 288 (and XXX new)
candidates with averaged grade $0<$G$<1.3$ (low probability sample)
which means - in the worst case, at least one of the inspector thought
the candidate is possibly a lens and in the best case, all three
inspectors thought the candidate is possibly a lens (that is,
a grade of 1)\footnote{If grades from the inspectors were found to be discrepant
by 2 or more, these were discussed and re-graded to resolve the
discrepancy.}. Further information on the low probability sample such as
their positions and images is available at
http://spacewarps.org/\#/projects/CFHTLS/. Note that if all of the inspectors gave
a grade of 0 to a candidate, then it is discarded from the sample.

There are a total of 91 candidates with $1.3\le$G$<2$ (medium
probability sample) out of which 30 are new. The quality of candidates
in this category is such that at least one of the inspectors thought the
candidate is most probably a lens (that is, a grade of 2) and a second inspector
thought this is possibly a lens (that is, a grade of 1). Among our high
probability sample (G$\ge$2), there are a total of 50 candidates out of
which 28 are new. In this category, the minimum grade by all of the
inspectors was 2 suggesting that the candidates are probably or almost
certainly lenses according to all of the inspectors. To avoid
duplication, further information on \sw candidates that were previously
identified in the literature is available at
http://spacewarps.org/\#/projects/CFHTLS/ whereas the sample of new lens
candidates with G$\ge 1.3$ (medium-high probability) is presented in this paper (see
\Sref{sec:results:newcand}).

In Table~\ref{tab:stats}, we give overall statistics of the systems
detected at \StageOne and \StageTwo. We give the total number of
detections of the known lens candidates, known lenses and the new lens
candidates at each stage.  We also give the recovery fractions for the
known samples and fraction of total detection for the new samples at
each stage. We find that all of the confirmed lenses found
at \StageOne are also recovered at \StageTwo whereas a small fraction of
the known lens candidates are rejected at \StageTwo. From the visually
inspected known lens sample at \StageTwo (P$> 0.3$), the experts gave a
grade of 1.3 and above to about 92\% (33 out of 36) of the systems. Overall,
the sample of new \sw lens candidates increased the sample of total
\cfhtls lens candidates by over 50\%.

In \Fref{fig:stackP}, we plot the distribution of false positives and
the high probability lens candidates, categorized by the lens experts,
as a function of the P value assigned by SWAP at the end of \StageTwo.
On average, the fraction of lens candidates is indeed an increasing
function of P. This shows that the \sw generated P values for the
subject are roughly correlated with the expert grades albeit with quite
some scatter.  We note that from P$\sim$0.75 onwards to lower P values,
the fraction of false positives starts to exceed the fraction of real
lens candidates. This could be a good threshold to choose to maximize
the purity of the final sample. However, we go with the choice of
P~$=$~0.3 as this gives a better completeness of 100\% for the ``known
lens'' sample instead of 67\% for P~$=$~0.75. Therefore, the new sample
should also have increased completeness which combined with expert
grading allows us to achieve further purity of our sample.

@@

%Note: $\dagger$ are systems found in \citet{Gavazzi2014} as part of the additional
